---
title: "HW Pstat"
output: pdf_document
---
1. This problem uses the data set UN11 from the alr4 package.
a) 

```{r}
library(alr4)
names(UN11)
pairs(~fertility+log(ppgdp) + pctUrban, data = UN11)
##From looking at all the scatterplots we can tell that Fertility and log(ppgdp) have a negative correlation.   ##Fertility and pctUrban has a negative correlation ## log(ppgdp) and pctUrban has a negative correlation
```

b) 

```{r}
lmfert <- lm(fertility~log(ppgdp)+pctUrban,data=UN11)
summary(lmfert)
#the coefficient of log(ppgdp) is siginificantly different from 0 as the p value is very low.
```

c) 

```{r}
k <- avPlots(lmfert)
##This give the partial regression plot : from here we can say that log(ppgdp) is useful as it shows a steep slope while pctUrban is neutral to fertility
### here we obtain the partial regression slope
h=lm(log(ppgdp)~pctUrban,data=UN11)

resi=h$residuals    ##for the residuals

G=lm(fertility~resi,data=UN11)

summary(G) 

##From both the fits it is evident the estimated coefficient of log(ppgdp) from the ordinary regression is same as the estimated slope of (ppgdp) from the added variable plot
```


2. 
).
a) Suppose that xi1 and xi2 are exactly related in that xi1 = 2.2xi2 for all i. For
example, xi2 could be weight in kilograms and xi1 weight in pounds for the ith individual. Describe the appearance of the added-variable plot for xi2 after
adjusting for xi1.


#the apperance on the added vaiable plot would be increased positively in a linear relationship, the slope would increase by2.2

b) Suppose instead that xi1 and xi2 are not perfectly correlated, but that Yi = 3xi1, i.e.
Yi
is perfectly correlated with xi1. Describe the appearance of the added-variable
plot for xi2.


##Without perfect correlaion the added variable would create a destruction in the linear relatinship and increase the error estimation between the predictors and response in a negative 3 power. 







